\ \break Automatikus korpuszépítés tulajdonnév-felismerés céljára

### 2013-01-04 paper/MSZNY2013/mszny_slides.tex
I don't know.

\subsection{Tulajdonnevek címkézése}
\begin{frame}{Tulajdonnevek címkézése}
  \bigskip
  \begin{itemize}
  \vitem Entity identification:
    \begin{itemize}
    \vitem Look up linked pages in the entity list
    \vitem References to the current page, if in the list
    \end{itemize}
  \vitem NE tagging: from the DBpedia--CoNLL category mapping
  \vitem Exceptions:
    \begin{itemize}
    \vitem Not entities: common nouns, date expressions, etc.
    \vitem Unmarked entities: link to already identified entities
    \vitem Special cases: derived words, first word in a sentence, etc.
    \end{itemize}
  \end{itemize}
\end{frame}

\subsection{Sentence Filtering}
\begin{frame}{Sentence Filtering}
  \bigskip
  We only include fully tagged sentences in the corpus.
  \smallskip
  \begin{itemize}
  \vitem Sentences that contain unknown links / uppercase words
  \vitem To filter incomplete sentences:
    \begin{itemize}
    \vitem Sentences without an EOS punctuation mark
    \vitem Sentences without a predicate (verb)
    \end{itemize}
  \end{itemize}
\end{frame}

>>>>

\subsection{Tulajdonnevek címkézése}
\begin{frame}{Tulajdonnevek címkézése}
  \bigskip
  \begin{itemize}
  \vitem Tulajdonnevek felismerése:
    \begin{itemize}
    \vitem Look up linked pages in the entity list
    \vitem References to the current page, if in the list
    \end{itemize}
  \vitem NE tagging: from the DBpedia--CoNLL category mapping
  \vitem Kivételek:
    \begin{itemize}
    \vitem Cikkek, amik nem entitások: nagybetűvel kell kezdődjön a szócikk
    \vitem Jelöletlen entitások: megpróbáljuk őket korábbi tulajdonnevekhez kötni
    \vitem Speciális esetek: tulajdonnév-köznév összetételek, mondatkezdő főnevek, stb.
    \end{itemize}
  \end{itemize}
\end{frame}

\subsection{Mondatok szűrése}
\begin{frame}{Mondatok szűrése}
  \bigskip
  Csak a teljesen felcímkézett mondatokat tartjuk meg. Eldobjuk:
  \smallskip
  \begin{itemize}
  \vitem azokat a mondatokat, amiben címkézetlen hivatkozások vagy nagybetűs szavak vannak
  \vitem a mondattöredékeket:
    \begin{itemize}
    \vitem amikben nincs mondatvégi írásjel
    \vitem állítmány nélküli mondatok %TODO: tényleg?
    \end{itemize}
  \end{itemize}
\end{frame}
